Approximation as Differentiation notes

### 2025-02-21 notes/definitions.tex
$\CMon$ is complete and cocomplete.

$\CMon$ is the category whose objects are the commutative monoids $M$ and morphisms $M \to M'$ are the
commutative monoid homomorphisms, with the trivial one-element monoid $\One$ as terminal object and binary
products $M \tensor M'$ given by the direct product of monoids.

>>>>

$\CMon$ is the category whose objects are the commutative monoids $M$ and morphisms $M \to M'$ are the
commutative monoid homomorphisms. $\CMon$ is symmetric closed monoidal, with the trivial one-element monoid
$\One$ as terminal object and tensor product $M \tensor M'$ given by the direct product of $M$ and $M'$. In
fact $\CMon$ is complete and cocomplete, inheriting all limits and colimits from $\Set$.
